Supplementary Materials for 'Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-05 analysis/supplementary materials/supplementary materials.Rmd
move sup figures to analysis/figures

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_1.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_2.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_3.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_4.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_5.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  outfile = here(
    "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/supplementary figures/Sparks_et_al_Supplementary_Figure_6.eps"
))
```

>>>>

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_1.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_2.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_3.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_4.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_5.eps"
))
```

@@

ggsave(
  filename = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  plot = p,
  width = 6,
  height = 6,
  units = "in",
  device = cairo_ps
)
embed_fonts(
  file = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  outfile = here(
    "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
  ),
  options = "-dEPSCrop"
)
include_graphics(path = here(
  "analysis/figures/Sparks_et_al_Supplementary_Figure_6.eps"
))
```
